%-------------------------
% Generic ATS-Optimized Resume – Prateek Verma
% Suitable for: SDE I/II, Full Stack, Backend, Platform, AI/ML Engineer roles
%-------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{geometry}

\geometry{top=0.42in, bottom=0.42in, left=0.5in, right=0.5in}

\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
\begin{document}

%---------- HEADER ----------
\begin{center}
  {\LARGE \textbf{Prateek Verma}} \\[4pt]
  \small Software Development Engineer -- Full Stack, Java, TypeScript, and Cloud Systems \\[4pt]
  +91 7877123418 \;$|$\;
  \href{mailto:prateek.2001.verma@gmail.com}{prateek.2001.verma@gmail.com} \;$|$\;
  \href{https://linkedin.com/in/prateek-verma-8125b3201}{linkedin.com/in/prateek-verma-8125b3201} \;$|$\;
  Bangalore, India
\end{center}

%---------- SUMMARY ----------
\section{Summary}
\small{
Software Development Engineer with 2+ years of experience in full stack development and backend platforms.\\
Strong in Java, Spring Boot, TypeScript, and REST API delivery across microservices and cloud-native systems.
}

%---------- SKILLS ----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt]
  \small{
    \item \textbf{Languages:} Java, TypeScript, JavaScript
    \item \textbf{Frameworks:} Spring Boot, React.js, Node.js, Express.js
    \item \textbf{Cloud:} AWS, Kubernetes, Docker, Helm, Crossplane
    \item \textbf{Databases:} SQL, PostgreSQL, MySQL
    \item \textbf{Tools:} REST APIs, Microservices, OOP, GitHub Actions, Backstage, Prometheus, Grafana, OpenTelemetry
  }
\end{itemize}

%---------- EXPERIENCE ----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Philips}{Bangalore, India}
    {Software Development Engineer I}{Apr 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Designed Ultrasound Fleet Manager features using Java, Spring Boot, React.js, and REST APIs across 7+ microservices.}
      \resumeItem{Optimized API latency with caching and query tuning, reducing response time 15\% (400ms $\rightarrow$ 340ms).}
      \resumeItem{Standardized GitHub Actions across 11+ repos and automated Backstage onboarding, cutting setup time 90\%.}
      \resumeItem{Implemented Prometheus, Grafana, and OpenTelemetry tracing to improve production monitoring and diagnosis.}
    \resumeItemListEnd

  \resumeSubheading
    {Philips}{Bangalore, India}
    {Software Development Intern}{Jun 2023 -- Apr 2024}
    \resumeItemListStart
      \resumeItem{Developed React.js and Node.js features for the Backstage Developer Portal, serving 1,000+ internal developers.}
      \resumeItem{Integrated AWS Secrets Manager with EKS via External Secrets Operator across 3+ deployments and reviews.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Backstage Scaffold Insight Viewer Plugin} $|$ \textit{TypeScript, React.js, Node.js}}{}
    \resumeItemListStart
      \resumeItem{Published an open-source Backstage plugin with analytics dashboards and REST API integrations for platform adoption.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{JSONCrack OSS Contribution (10K+ Stars)} $|$ \textit{React.js, JavaScript, Production Debugging}}{}
    \resumeItemListStart
      \resumeItem{Resolved a production crash in the Tree View by fixing unsafe state initialization for thousands of users.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Lovely Professional University}{Punjab, India}
    {B.Tech in Computer Science and Engineering \textnormal{$|$ GPA: 8.41 / 10}}{Jul 2020 -- May 2024}
\resumeSubHeadingListEnd

%---------- CERTIFICATIONS ----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
  \small{\item AWS Certified Cloud Practitioner}
\end{itemize}

\end{document}