%-------------------------
% Tailored Resume – Prateek Verma – Optum
% Role: Full Stack Engineer (Java Spring Boot & React)
%-------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{geometry}

\geometry{top=0.42in, bottom=0.42in, left=0.5in, right=0.5in}

\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
\begin{document}

%---------- HEADER ----------
\begin{center}
  {\LARGE \textbf{Prateek Verma}} \\[4pt]
  \small Full Stack Engineer -- Java Spring Boot, React \& Cloud Technologies \\[4pt]
  +91 7877123418 \;$|$\;
  \href{mailto:prateek.2001.verma@gmail.com}{prateek.2001.verma@gmail.com} \;$|$\;
  \href{https://linkedin.com/in/prateek-verma-8125b3201}{linkedin.com/in/prateek-verma} \;$|$\;
  Bangalore, India
\end{center}

%---------- PROFESSIONAL SUMMARY ----------
\section{Professional Summary}
\small{
Full Stack Engineer with 2+ years of experience developing scalable, high-performance web applications using Java Spring Boot, React, and cloud technologies. Proficient in building and fine-tuning RESTful APIs, translating designs into high-quality code, and optimizing components for maximum performance. Proven track record of delivering innovative solutions, collaborating cross-functionally, and ensuring code quality through structured reviews. AWS Certified with hands-on experience in containerization, CI/CD pipelines, and Agile development methodologies.
}

%---------- KEY SKILLS ----------
\section{Key Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt]
  \small{
    \item \textbf{Languages:} Java, JavaScript, TypeScript
    \item \textbf{Frontend:} React.js, Component-Based Applications, HTML, CSS
    \item \textbf{Backend:} Spring Boot, RESTful APIs, Microservices, Hibernate, OOP, Design Patterns
    \item \textbf{Databases:} SQL, MySQL, PostgreSQL, RDBMS
    \item \textbf{Cloud \& DevOps:} CI/CD, Jenkins, GitHub Actions, AWS (EKS, ECR, S3, Secrets Manager), Kubernetes, Docker
    \item \textbf{Tools:} Git, Linux, Prometheus, OpenTelemetry, Grafana
  }
\end{itemize}

%---------- PROFESSIONAL EXPERIENCE ----------
\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Philips}{Bangalore, India}
    {Software Development Engineer I}{Apr 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Developed new user-facing features using React.js and Java Spring Boot, translating designs and wireframes into high-quality code for the Ultrasound Fleet Manager platform.}
      \resumeItem{Built and fine-tuned RESTful APIs and microservices, optimizing performance and ensuring scalability across distributed application modules.}
      \resumeItem{Implemented CI/CD pipelines using Jenkins and GitHub Actions, automating deployments and improving development velocity.}
      \resumeItem{Collaborated with cross-functional teams to ensure alignment with business objectives, participating in grooming sessions and providing technical guidance to junior engineers.}
      \resumeItem{Handled production support, resolving incident tickets and conducting root cause analysis to ensure system reliability.}
    \resumeItemListEnd

  \resumeSubheading
    {Philips}{Bangalore, India}
    {Software Development Intern}{Jun 2023 -- Apr 2024}
    \resumeItemListStart
      \resumeItem{Developed full-stack features using React.js and Node.js for the Backstage Developer Portal, building reusable component libraries and REST API integrations serving 1,000+ internal developers.}
      \resumeItem{Implemented AWS Secrets Manager integration with EKS via External Secrets Operator across 3+ production deployments, ensuring secure and scalable infrastructure.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Backstage Scaffold Insight Viewer Plugin} $|$ \textit{Open Source, TypeScript, React.js, Node.js}}{}
    \resumeItemListStart
      \resumeItem{Published open-source full-stack plugin with REST API integrations and real-time analytics dashboards; adopted by engineering teams for monitoring developer tooling reliability.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Naukri Resume Action} $|$ \textit{GitHub Actions, Shell Scripting, CI/CD Automation}}{}
    \resumeItemListStart
      \resumeItem{Built and published a reusable GitHub Actions workflow using shell scripting to automate resume uploads on a schedule; implemented secure credential handling and self-hosted runner support for reliable DevOps automation.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{JSONCrack OSS Contribution (10K+ Stars)} $|$ \textit{React.js, JavaScript, Production Debugging}}{}
    \resumeItemListStart
      \resumeItem{Resolved a production crash in a widely-used open-source project via safe state initialization guard conditions, eliminating null reference errors for thousands of users and improving application stability.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Lovely Professional University}{Punjab, India}
    {B.Tech in Computer Science and Engineering \textnormal{$|$ GPA: 8.41 / 10}}{Jul 2020 -- May 2024}
\resumeSubHeadingListEnd

%---------- CERTIFICATIONS ----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
  \small{\item AWS Certified Cloud Practitioner}
\end{itemize}

\end{document}
